---
title: "analysis script famous voices"
author: "Elise Kanber"
date: "16/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description: 

This is an example data analysis pipeline for an experiment ran as part of my PhD.
Steps involved: 
- Merging multiple CSVs containing participant data using a for loop
- Cleaning the data using dplyr functions 
          - remove participants who were performing below a particular threshold
          - remove "time out" trials (this was a reaction time task and if participants were too slow they were timed out)
          - remove reaction times that were too fast (unlikely to be true reaction times)
          - only keep columns of interest
- set up linear mixed effects models comparing a model that contains all fixed and random effects to a model with the              fixed effect of interest removed
- run pairwise multiple comparisons using emmeans()
- Plot the model estimates and effects 
- Print estimates and confidence intervals (sjPlot)

Load packages: 
```{r}
library(tidyverse)
library(lme4)
library(emmeans)
library(effects)
library(ggplot2)
library(afex)
library(yarrr)
library(sjPlot)
```

Our data are contained in multiple csv files that have the same column names. First we need to combine these files: 
First, make sure the csvs you want to combine are all in the same folder, and that nothing else is in this folder.
```{r}
# Create list of files in folder that you want to merge

my_files<- list.files(path/to/merge/folder)

my_data<-data.frame() # Create empty data frame for combined data
nsub <- 30 # Change to your sample size (should match number of files you want to merge)

# Clean and combine csv files

for (i in 1:nsub)
  
{myfile<-my_files[i]
this.file<-read.csv(paste0("path/to/merge/folder",myfile))

# Here you can list the columns you want to keep from the CSVs 
this.file<-select(this.file, Participant.Public.ID, Participant.Status, branch.k895, Spreadsheet, Trial.Number, Screen.Name, Zone.Type, Reaction.Time, 
                  Response, Correct, Timed.Out, display, spaceFix, cue, reward.magnitude, stim_type, threshold)
# this.file<- filter(this.file, Zone.Type == "response_button_text" | Zone.Type == "response_keyboard")
my_data<-rbind(my_data, this.file)
}

write.csv(my_data,"raw_merged.csv")

```



Now we can read in the data (or use "my_data" variable above)
```{r}
data <- read.csv("raw_merged.csv")
questionnaires <- read.csv("questionnaire_merged.csv")
```

Clean data using filter and select:
```{r}

cleaned <- filter(data, display == "main" & Screen.Name == "Screen 2")

cleaned$Participant.Public.ID <- droplevels(cleaned$Participant.Public.ID)

# Remove participants that timed out over a 1/3 of the time

timeout_summary <- cleaned %>% group_by(Participant.Public.ID) %>% 
  summarise(ntimeouts = sum(Timed.Out, na.rm = TRUE), pcnt = (ntimeouts/72)*100) %>% 
  mutate(exclude = if_else(ntimeouts > 24, 1, 0))

mean_timeout <- timeout_summary %>% summarise(meantimeout = mean(ntimeouts))

# Create a separate dataframe including the participant id and whether this participant should be excluded. 
to_exclude <- select(timeout_summary, Participant.Public.ID, exclude)


# join to_exclude to cleaned
merged <- inner_join(cleaned, to_exclude)

```

Select only the columns we want, and also filter to only get the fast enough RT trials (i.e. filter out the timeouts): 
```{r}
dat <- merged %>% select(Participant.Public.ID, reward.magnitude, Reaction.Time, display, Response, Screen.Name, exclude, stim_type, branch.k895, threshold, Spreadsheet)


# Extract the counterbalancing order: 

dat$CB_order <- dat$Spreadsheet %>% 
  recode(beyonce_CB1 = "CB1", beyonce_CB2 = "CB2", beyonce_CB3 = "CB3", harry_CB1 = "CB1", harry_CB2 = "CB2", harry_CB3 = "CB3", taylor_CB1 = "CB1", taylor_CB2 = "CB2", taylor_CB3 = "CB3", justin_CB1 = "CB1", justin_CB2 = "CB2", justin_CB3 = "CB3")

# dat <- dat %>% group_by(Participant.Public.ID) %>% mutate(n = 1:n()) %>% mutate(half = if_else(n == 1:36, 1, 2))


# # Cleaned data but including timeouts, to be used to analyse timeouts:
# dat2 <- dat %>% filter(exclude == 0)
# dat2 <- dat2 %>%  filter(Participant.Public.ID != "p115", Participant.Public.ID != "p120", Participant.Public.ID != "p129", Participant.Public.ID != "p105", Participant.Public.ID != "p202", Participant.Public.ID != "p242", Participant.Public.ID != "p126", Participant.Public.ID != "p262")


# "p146" "p214"

# dat2$Participant.Public.ID <- droplevels(dat2$Participant.Public.ID)


# Include only trials that were not timeouts: 
dat <- dat %>% filter(Response == "Press" & exclude == 0)


any_NAs <- dat %>% 
  group_by(Participant.Public.ID) %>% 
  summarise(mean = mean(threshold))

dat <- dat %>% filter(Participant.Public.ID != "p115", Participant.Public.ID != "p120", Participant.Public.ID != "p129", Participant.Public.ID != "p105", Participant.Public.ID != "p202", Participant.Public.ID != "p242", Participant.Public.ID != "p126", Participant.Public.ID != "p262")


```


Include only RTs that were 150ms or longer:
```{r}
# Convert RT into numeric: 
dat$Reaction.Time <- as.character(dat$Reaction.Time)
options(digits = 9)
dat$Reaction.Time <- as.numeric(dat$Reaction.Time)

finaldat <- dat %>% filter(Reaction.Time > 149.99)

finaldat$Participant.Public.ID <- droplevels(finaldat$Participant.Public.ID)
finaldat$reward.magnitude <- droplevels(finaldat$reward.magnitude)



```

Set up the models:
```{r}
full <- lmer(Reaction.Time ~ reward.magnitude + (1|Participant.Public.ID), data = finaldat, REML = FALSE)
reduced <- lmer(Reaction.Time ~   (1|Participant.Public.ID), data = finaldat, REML = FALSE)

anova(full,reduced)

summary(full)

```
```{r}
emmeans(full, (pairwise ~ reward.magnitude), adjust = "none", pbkrtest.limit = 4881)
```

```{r}
e <- allEffects(full)
print(e)
plot(e)
```
Raw means: 
```{r}
raw_means <- finaldat %>% group_by(reward.magnitude) %>% summarise(mean = mean(Reaction.Time), SD = sd(Reaction.Time))
View(raw_means)
```

Estimates and confidence intervals: 
```{r}
library(sjPlot)
plot_model(full)
tab_model(full, file = "SID_famous.html")
```


Analysis to examine whether there is a relationship between how pleasant the listener rated the voice recordings and how fast they responded in a reaction time task to these voices: 

# Filter the questionnaire data, and then join it to the main data: 
```{r}
questionnaires$Question.Key <- questionnaires$Question.Key %>% recode(beyonce_pleasantness_rating = "large_pleasantness_rating", harry_pleasantness_rating = "large_pleasantness_rating", Taylor_pleasantness_rating = "large_pleasantness_rating", Justin_pleasantness_rating = "large_pleasantness_rating", Simone_pleasantness_rating = "small_pleasantness_rating", Max_pleasantness_rating = "small_pleasantness_rating", Julie_pleasantness_rating = "small_pleasantness_rating", Sean_pleasantness_rating = "small_pleasantness_rating")
 
pleasantness <- filter(questionnaires, Question.Key == "large_pleasantness_rating" | 
                         Question.Key == "small_pleasantness_rating" |
                         Question.Key == "tone_pleasantness_rating")


# Recode the column names so that I can merge the questionnaire data with the main data: 
# Index into the levels and rename each one
levels(pleasantness$Question.Key)[levels(pleasantness$Question.Key) == "large_pleasantness_rating"]  <- "large"
levels(pleasantness$Question.Key)[levels(pleasantness$Question.Key) == "small_pleasantness_rating"] <- "small"
levels(pleasantness$Question.Key)[levels(pleasantness$Question.Key) == "tone_pleasantness_rating"] <- "none"
pleasantness$rating <- pleasantness$Response
pleasantness$reward.magnitude <- pleasantness$Question.Key

pleasantness <- select(pleasantness, Participant.Public.ID, rating, reward.magnitude)

RTs_with_ratings <- inner_join(finaldat, pleasantness)
RTs_with_ratings <- mutate(RTs_with_ratings, grouped_rating = if_else(rating == "1" | rating == "2" | rating == "3", "low", if_else(rating == "4" | rating == "5" | rating == "6", "medium", "high")))

RTs_with_ratings$Participant.Public.ID <- as.factor(RTs_with_ratings$Participant.Public.ID)

```

Set up models: 
```{r}
pleasant_full <- lmer(Reaction.Time ~ reward.magnitude*grouped_rating + (1|Participant.Public.ID), data = RTs_with_ratings, REML = FALSE)


pleasant_reduced <- lmer(Reaction.Time ~ reward.magnitude + grouped_rating + (1|Participant.Public.ID), data = RTs_with_ratings, REML = FALSE)


anova(pleasant_full,pleasant_reduced)

# emmeans(pleasant_full, (pairwise ~ reward.magnitude*grouped_rating), adjust = "none")
summary(pleasant_full)

```
No interaction:
```{r}
grouped_rating_eff <- lmer(Reaction.Time ~ reward.magnitude + (1|Participant.Public.ID), data = RTs_with_ratings, REML = FALSE)

anova(pleasant_reduced, grouped_rating_eff)

emmeans(pleasant_reduced, (pairwise ~ grouped_rating), adjust = "none")
summary(pleasant_reduced)


reward_eff <- lmer(Reaction.Time ~ grouped_rating + (1|Participant.Public.ID), data = RTs_with_ratings, REML = FALSE)

anova(pleasant_reduced, reward_eff)




```
Looking at whether there is an effect of pleasantness ratings on reaction times: 
```{r}
full <- lmer(Reaction.Time ~ grouped_rating + (1|Participant.Public.ID), data = RTs_with_ratings, REML= FALSE)
reduced <- lmer(Reaction.Time ~ (1|Participant.Public.ID), data = RTs_with_ratings, REML = FALSE)
anova(full, reduced)
summary(full)

emmeans(full, (pairwise ~ grouped_rating), adjust = "none")
```


```{r}
ggplot(RTs_with_ratings, aes(x=rating, y=Reaction.Time)) + geom_point()
```



Mean ratings and whether these are significantly different for the different conditions:
ANOVA
```{r}
library(afex)
library(broom)
# pleasantness$rating <- droplevels(pleasantness$rating)
pleasantness$rating <- as.character(pleasantness$rating)
pleasantness$rating <- as.numeric(pleasantness$rating)

# pleasantness <- pleasantness %>%  mutate(reward_num = recode(reward.magnitude, "large" = 3, "small" = 2, "none" = 1))
mod <- aov_ez(id = "Participant.Public.ID", # the column containing the subject IDs
              dv = "rating", # the DV 
              within = "reward.magnitude", # the between-subject variable
              es = "pes", # sets effect size to partial eta-squared
              type = 3, # this affects how the sum of squares is calculated, set this to 3
              data = pleasantness)

anova(mod)
mod_output <- (mod$anova_table) %>% tidy()
mod_output

mod_pairwise <- emmeans(mod$aov, pairwise ~ reward.magnitude, adjust = "none")
mod_pairwise

# graph: 

mean_pleasant <- pleasantness %>% 
  group_by(reward.magnitude) %>% 
  summarise( sd = sd(rating), rating = mean(rating))



library(ggsignif)


#
pdf(file = "/Users/carolynmcgettigan/Documents/Thesis/CHAPTER_4/CH4_pleasantness_ratings_pos_dodge.pdf", # The directory you want to save the file in
width = 8, # The width of the plot in inches
height = 6)
ggplot(mean_pleasant, aes(x = reward.magnitude, y = rating)) + 
  geom_bar(stat = "identity", alpha = 0.8, width = 0.9, fill = c("#a01a58", "#723c70", "#5c4d7d")) + 
  geom_point(data = pleasantness, size = 0.9, alpha = 0.4, aes(fill = "black"), position = position_dodge2(width=0.2), show.legend = FALSE) + 
  # geom_errorbar(aes(ymin = rating - sd, ymax = rating + sd), width = 0.1) +
  theme_classic() + 
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9), limits = c(0,11)) + 
  labs(x = "Outcome", y = "Pleasantness Rating") + 
  scale_x_discrete(labels = c("Musical\nIdol", "Athlete", "Pure\n Tone")) +
geom_signif(comparisons = list(c("large", "small")), annotations="***", y_position = 10, size = 0.9, textsize = 10,vjust=0.4,
              map_signif_level=TRUE) +
  geom_signif(comparisons = list(c("large", "none")), annotations="***", y_position = 11,textsize = 10, size = 0.9, vjust=0.4, map_signif_level = TRUE) +
  geom_signif(comparisons = list(c("small", "none")), annotations="***", textsize = 10, size = 0.9, vjust=0.1, y_position = 9.5, map_signif_level = TRUE) +
 # ylim(0,10) + 
  theme(axis.text.x = element_text(face = "bold", size = 16, angle = 0, colour = "black"), 
        axis.text.y = element_text(face = "bold", size = 16, angle = 0, colour = "black"),
     axis.title = element_text(face = "bold", size = 16, colour = "black"),
     axis.title.x = element_text(margin = margin(t=20)),
        axis.title.y = element_text(margin = margin(r=20)))
dev.off()



```


Exploratory Analyses: 

Examining whether there were differences in the number of timeout trials between the three conditions (were listeners just trying less hard for certain voices): 
```{r}
dat2 <- merged %>% select(Participant.Public.ID, reward.magnitude, Reaction.Time, display, Response, Screen.Name, exclude, stim_type, branch.k895, threshold, Spreadsheet)

dat2 <- dat2 %>% filter(Participant.Public.ID != "p115", Participant.Public.ID != "p120", Participant.Public.ID != "p129", Participant.Public.ID != "p105", Participant.Public.ID != "p202", Participant.Public.ID != "p242", Participant.Public.ID != "p126", Participant.Public.ID != "p262")

# Extract the counterbalancing order: 

dat2$CB_order <- dat2$Spreadsheet %>% 
  recode(beyonce_CB1 = "CB1", beyonce_CB2 = "CB2", beyonce_CB3 = "CB3", harry_CB1 = "CB1", harry_CB2 = "CB2", harry_CB3 = "CB3", taylor_CB1 = "CB1", taylor_CB2 = "CB2", taylor_CB3 = "CB3", justin_CB1 = "CB1", justin_CB2 = "CB2", justin_CB3 = "CB3")

timeout_dat <- mutate(dat2, dv = if_else(Response == "Press", 0, 1))

timeout_dat <- filter(timeout_dat, exclude == 0)
```
 
```{r}
# Convert RT into numeric: 
timeout_dat$Reaction.Time <- as.character(timeout_dat$Reaction.Time)
options(digits = 9)
timeout_dat$Reaction.Time <- as.numeric(timeout_dat$Reaction.Time)

timeouts <- select(timeout_dat, "Participant.Public.ID", "dv", "reward.magnitude") %>%  group_by(Participant.Public.ID, reward.magnitude) %>% summarise(dv = mean(dv))
timeouts$reward.magnitude <- droplevels(timeouts$reward.magnitude)



# timeout_dat$dv <- as.factor(timeout_dat$dv)

# timeout_dat_final <- timeout_dat %>% filter(Reaction.Time > 149.99)

# timeout_dat_final$Participant.Public.ID <- droplevels(timeout_dat_final$Participant.Public.ID)

# #
# mod <- aov_ez(id = "Participant.Public.ID", # the column containing the subject IDs
#               dv = "dv", # the DV
#               within = "reward.magnitude", # the between-subject variable
#               es = "pes", # sets effect size to partial eta-squared
#               type = 3, # this affects how the sum of squares is calculated, set this to 3
#               data = timeouts)
# 
# anova(mod)
# mod_output <- (mod$anova_table) %>% tidy()
# mod_output
# 
# mod_pairwise <- emmeans(mod$aov, pairwise ~ reward.magnitude, adjust = "FDR")
# mod_pairwise
# 
# mean_timeout <- timeout_dat %>%
#   group_by(reward.magnitude, Participant.Public.ID) %>%
#   summarise(sum = sum(dv)) %>%
#   summarise(mean = mean(sum))
# 
# ggplot(mean_timeout, aes(x = reward.magnitude, y = mean)) +
#   geom_bar(stat = "identity", alpha = 0.8, fill = "black") +
#   # geom_point(data = timeout_dat, size = 0.85, alpha = 0.6, aes(color = factor(Participant.Public.ID)), show.legend = FALSE, position = position_dodge(width = 0.2)) +
#   theme_classic() +
#   labs(x = "incentive magnitude", y = "mean number of timeouts") +
#  # ylim(0,9) +
#     theme(axis.text.x = element_text(face = "bold", size = 16, angle = 0),
#         axis.text.y = element_text(face = "bold", size = 16, angle = 0),
#      axis.title = element_text(face = "bold", size = 16))

```

Set up the models:
```{r}
# timeout_dat$dv <- as.factor(timeout_dat$dv)
timeout_dat$reward.magnitude <- droplevels(timeout_dat$reward.magnitude)
timeout_full <- glmer(dv ~ reward.magnitude + (1|Participant.Public.ID), data = timeout_dat, family = "binomial")

timeout_reduced <- glmer(dv ~ (1|Participant.Public.ID), data = timeout_dat, family = "binomial")


anova(timeout_full,timeout_reduced)



```


```{r}
emmeans(timeout_full, (pairwise ~ reward.magnitude), adjust = "FDR")
```

```{r}
library(effects)
e <- allEffects(timeout_full)
print(e)
plot(e)
```


Trivia scores and reward magnitude on reaction times: 
is there an interaction between the famous voice and how much trivia knowledge a listener has, on the participant's reaction time? 
E.g. are participants faster if they score highly on trivia AND it is a voice they care about?
```{r}
trivia <- questionnaires %>% 
  filter(Question.Key == "Q1" | Question.Key == "Q2" | Question.Key == "Q3"| Question.Key == "Q4"| Question.Key == "Q5"| Question.Key == "Q6"| Question.Key == "Q7"| Question.Key == "Q8"| Question.Key == "Q9"| Question.Key == "Q10")

# Group by participant and work out the total score: 
trivia_scores <- trivia %>% 
  group_by(Participant.Public.ID) %>% 
  summarise(total_score = sum(correct, na.rm = TRUE))

summary_dat <- finaldat %>% 
  group_by(Participant.Public.ID, reward.magnitude)


dat_with_trivia <- inner_join(finaldat, trivia_scores)

dat_with_trivia$total_score <- as.factor(dat_with_trivia$total_score)

trivia_interact <- lmer(Reaction.Time ~ reward.magnitude*total_score + (1|Participant.Public.ID), data = dat_with_trivia, REML = FALSE)
trivia_reduced <- lmer(Reaction.Time ~ reward.magnitude + total_score + (1|Participant.Public.ID), data = dat_with_trivia, REML = FALSE)
anova(trivia_interact, trivia_reduced)

summary(trivia_interact)
emmeans(trivia_interact, (pairwise ~ reward.magnitude*total_score), adjust = "none")

```

```{r}
trivia_eff <- lmer(Reaction.Time ~ reward.magnitude + (1|Participant.Public.ID), data = dat_with_trivia, REML = FALSE)

anova(trivia_reduced, trivia_eff)

emmeans(trivia_reduced, (pairwise ~ total_score), adjust = "none")
```

```{r}
y <- finaldat %>% 
group_by(Participant.Public.ID, branch.k895) %>% 
summarise(mean = mean(Reaction.Time, na.rm = TRUE))

z <- y %>% group_by(branch.k895) %>% summarise(n = n())

v <- finaldat %>% 
  group_by(Participant.Public.ID) %>% 
  summarise(mean = mean(Reaction.Time, na.rm = TRUE))
w <- v %>%  summarise(n = n())
```


Working out trivia scores per participant and per group/celeb: 
```{r}
dat_with_trivia <- inner_join(finaldat, trivia_scores)
trivia <- dat_with_trivia %>% group_by(Participant.Public.ID, branch.k895) %>% summarise(total_score = mean(total_score))
summary <- trivia %>% group_by(branch.k895, total_score) %>% summarise(n = n())

general_summary <- trivia %>%  group_by(total_score) %>% summarise(n = n())

# Removing participants that performed poorly on the trivia quiz: 

data_rm_poor_scorers <- dat_with_trivia %>% filter(total_score > 6)

raw_means <- data_rm_poor_scorers %>% group_by(reward.magnitude) %>% summarise(mean = mean(Reaction.Time))
 
# Seeing if this affects the results (it doesn't): 
full <- lmer(Reaction.Time ~ reward.magnitude + (1|Participant.Public.ID), data = data_rm_poor_scorers, REML = FALSE)
reduced <- lmer(Reaction.Time ~ (1|Participant.Public.ID), data = data_rm_poor_scorers, REML = FALSE)

anova(full, reduced)

emmeans(full, (pairwise ~ reward.magnitude), adjust = "FDR")


```


