---
title: "Re-naming files"
author: "Elise Kanber"
date: "21/04/2022"
output: html_document
---
##########################################################################################################
A script to rename files. Here we used files from the freely-available Saarbruecken voice database. Files were renamed such that the new file names are more intuitive/contain useful information such as the age, sex, and vocal health of the speaker. 
##########################################################################################################

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages:
```{r}
library(dplyr)
library(tidyverse)
library(readr)
# install.packages("sjmisc")
library(sjmisc)
```

## First, I want to extract the session ID from the audio file names and then save this to a new column called session.id (to match a column in another existing file, so that eventually we can inner_join())
Read in the csv file containing the audio file names:
```{r}
audiofiles <- read.csv("/Users/e.kanber/OneDrive - University College London/postdoc/saarbruecken voice database/audio_files.csv")
```

## The first characters in the audio file name are the session id. I want to save off the numbers, so I use "parse_number". Can also use substr()
```{r}
# audiofiles <- audiofiles %>% mutate(session.id = substr(audio, 1, 3))

audiofiles <- audiofiles %>% mutate(session.id = parse_number(audio))
```

## Next, I want to read in the .csv file containing the speaker demographic information:
```{r}
demographics <- read.csv("/Users/e.kanber/OneDrive - University College London/postdoc/saarbruecken voice database/database.csv")
```

## Join together the two dataframes: 
```{r}
data <- inner_join(audiofiles, demographics)

# Make the recording type (healthy or pathological) more meaningful
data <- data %>% mutate(recording.type = if_else(recording.type == "n", "hlth", "path"))

# Create a new column that includes whether the recording is an electroglottograph recording (egg) or not. Rows will either contain "-egg" or be left blank. 
data <- data %>% mutate(egg = if_else(grepl("egg", audio, fixed=TRUE), "-egg", ""))

data <- data %>% mutate(old = audio)

data$audio <- gsub("-egg.wav", "", data$audio)
data$audio <- gsub(".wav", "", data$audio)

# Make the Sex of the speaker more meaningful (m/f)
data <- data %>% mutate(sex = if_else(sex == "w", "f", "m"))
```

## New file names: 
```{r}
data <- data %>% mutate(new_name = paste0(audio, "_", age, sex, "-", recording.type, egg, ".wav"))
```


## Select particular columns: 
```{r}

data$audiofile <- data$new_name
data <- data %>% mutate(recording.type = if_else(recording.type == "hlth", "healthy", "pathological"))
data$original.filename <- data$old
database <- data %>% select(audiofile, original.filename, recording.type, sex, age, pathology, notes.on.pathology, participant.id, date.of.recording)
```
 
## Save database to csv file with new filenames
```{r}
write.csv(database, "Saarbrücken Voice Database.csv")
```

## Filter for file naming - e.g keep only the female healthy audio files. 
```{r}
filtered <- data %>% filter(recording.type == "pathological" & sex == "m")
```


## Rename files in directory:
```{r}
# filenames_old <- list.files("/Users/e.kanber/OneDrive - University College London/postdoc/saarbruecken voice database/female_healthy/")

my_path <- "/Users/e.kanber/OneDrive - University College London/postdoc/saarbruecken voice database/male_pathological/"

# filenames_new <- paste0(data$audio, "_", data$age, data$sex, "-", data$recording.type, data$egg, ".wav")
for(x in 1:nrow(filtered)){
file.rename(paste0(my_path, filtered$old[x]),       # Rename files
            paste0(my_path, filtered$new_name[x]))

 }
# lapply()
```
