---
title: 'Fill spreadsheets'
author: "Elise Kanber"
date: "26/10/2022"
output: html_document


### Folder structure ### 
#      2_Stimuli_Clips > LUCID > PPT_FEMALES/PPT_MALES > ppid > RMS > Examples
# Parameters need to be set in the third code chunk

# Requires templates to be available for filling in (code for creating these at the bottom of this script)

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load in packages: 
```{r}
library(tidyverse)
library(dplyr)
library(stringr)
# install.packages("tuneR")
# library(tuneR)
options(scipen=999) # so that we won't get scientific notation 


```

# Fill out some parameters: 
```{r}
id <- "pp01"                    # What is the participant ID? 
cb <-  "3"                      # Which counterbalancing order do we want? 
sex <- "f"                      # What is the sex of the participant's friend/partner/sibling? 
pname <- "Frankie"              # Name of the friend/partner/sibling. 

basedir <- paste0("/Users/e.kanber/Filestore/Research3/SHaPS/VoCoLab(Carolyn_McGettigan)/FAMILIARITY RSA/Stimuli/")
                                # Set the base directory to be accurate for your machine. 

```
# Set up other params and directories (shouldn't need to change these)
```{r}

# This tells R whether to look for the stimuli in the male or female voice clips folders. 
if(sex == "f"){                 
 ppfolder      = "PPT_FEMALES"
 lucidfolder   = "LUCID_FEMALES"
} else {
  ppfolder     = "PPT_MALES"
  lucidfolder  = "LUCID_MALES"
}

templatedir      <- paste0(basedir, "UsefulScripts/gorilla_templates/")
seqdir           <- paste0(basedir, "LUCID/2_StimuliClips/", ppfolder, "/", id, "/RMS/Examples/")
stimdir          <- paste0(basedir, "LUCID/2_StimuliClips/", ppfolder, "/", id, "/RMS/")
outdir           <- paste0(basedir,"LUCID/3_GorillaSpreadsheets/")
scandir          <- paste0(stimdir, "Scanner/")

```

# Read in the appropriate Gorilla template csv
```{r}
setwd(templatedir)
sheet <- read.csv(paste0("template_", sex, "_", cb, ".csv"))

# substitute FRIEND for the relevant name (participant's partner/friend/sibling's name)
sheet <- sheet %>%                                            
         mutate(text = gsub("FRIEND", pname, text)) %>% 
         mutate(CORRECT = gsub("FRIEND", pname, CORRECT)) %>% 
         mutate(ANSWER = gsub("FRIEND", pname, ANSWER)) %>% 
         mutate(A = gsub("FRIEND", pname, A))

```

# Read in the sequence files (two 6-clip sequences)
```{r}

# List all of the .wav files in the shortlist directory (recursive search)
stims <- data.frame(Filename = list.files(path=seqdir, pattern = "\\.mp3$", recursive = TRUE)) 

stims <- stims %>% filter(str_detect(Filename, "List")) %>%           # Keep the files that contain the string "List"
         mutate(Filename = gsub("Examples/", "", Filename))   # Remove the folder name (Examples/) from the filename 
stims <- droplevels(stims)

# stims[nrow(stims) + 1,1] <- stims[1,1]  # Don't need this anymore. 

```

# Paste the sequences to the correct positions in the dataframe
```{r}
sheet <- sheet %>% 
    mutate(audio = sub("SEQUENCE2", stims$Filename[2], audio)) %>% # Replace "SEQUENCE2" with the correct filename.
    mutate(audio = sub("SEQUENCE", stims$Filename[1], audio)) 
```

# Read in the 80 stimuli from the participant's FRIEND: 
```{r}
setwd(stimdir)

stimuli <- data.frame(Filename = list.files(path=stimdir, pattern = "\\.mp3$", recursive = FALSE)) # read in the list of stimuli 
```

# Fill rows with new stimuli 
```{r}
data <- sheet 

# Fill the rows with the stimuli where the name in the ANSWER column is the participant's friend's name (pname)
data$audio[data$ANSWER == pname] <- as.character(stimuli$Filename)

data <- replace(data, is.na(data), '')

```

# Save file as csv 
```{r}
setwd(outdir)
write.csv(data,paste0(id, "_spreadsheet_", sex, "_", cb, ".csv"), row.names = FALSE)
```


# Refresher training 
```{r}
setwd(templatedir)

# Read in the refresher template (includes the text info)
refresh <- read.csv("template_refresher.csv")
refresh <- replace(refresh, is.na(refresh), '')
head <- data %>% select("randomise_blocks", "randomise_trials", "display", "audio", "ANSWER")
head <- head[1:13,]


joined <- cbind(head, refresh)

# Subset the data from the familiarity training to include only the first block

data_subset <- data %>% 
  filter(display == "block1" | display == "block1_end" | display == "end")

# bind the two together 

refresh_spreadsheet <- rbind(joined, data_subset)
refresh_spreadsheet <- replace(refresh_spreadsheet, is.na(refresh_spreadsheet), '')

# write to csv 
setwd(outdir)
write.csv(refresh_spreadsheet, paste0(id, "_refresher_", sex, "_", cb, ".csv"), row.names = FALSE)

```

# Alex and Charlie voices
```{r}
# MRI_sheet <- read.csv("")
if(sex == "f"){
  if(cb == "1" | cb == "4"){
    Charlie <- "F22" 
  } else if (cb == "2" | cb == "6"){
    Charlie <- "F15"
  } else if (cb == "3" |cb == "5") {
    Charlie <- "F11"
  }
}

if (sex == "m") {
    if(cb == "1" | cb == "4") {
      Charlie <- "M26"
      } else if (cb == "2" | cb == "6") {
      Charlie <- "M17" 
      }  else if (cb == "3" | cb == "5") {
        Charlie <- "M10"
      }
}



if(sex == "f") {
  if(cb == "1" | cb == "2") {
    Alex <- "F11" 
  } else if (cb == "3" | cb == "4") {
    Alex <- "F15" 
  } else if (cb == "5" | cb == "6") {
    Alex <- "F22" 
  }
}

if(sex == "m"){
    if (cb == "1" | cb == "2") {
      Alex <- "M10"
    } else if (cb == "3" | cb == "4") {
      Alex <- "M17"
    } else if (cb == "5" | cb == "6") {
      Alex <- "M26"
    }
}
```


# Read in the scanner stimuli
```{r}
# setwd(scandir)
fdir        <- paste0(basedir, "LUCID/2_StimuliClips/", lucidfolder, "/", Alex, "/RMS/Scanner")
ufdir       <- paste0(basedir, "LUCID/2_StimuliClips/", lucidfolder, "/", Charlie, "/RMS/Scanner")

pf_stims    <- data.frame(Filename = list.files(path=scandir, pattern = "\\.wav$", recursive = FALSE))
f_stims     <- data.frame(Filename = list.files(path=fdir, pattern = "\\.wav$", recursive = FALSE))
uf_stims    <- data.frame(Filename = list.files(path=ufdir, pattern = "\\.wav$", recursive = FALSE))

# Bind the rows to create a list of file names (to be read in by MATLAB)
joined      <- rbind(pf_stims, f_stims, uf_stims) 

# FileDir = paste0("/Users/carolynmcgettigan/Documents/familiarity/")
# 
# if (!dir.exists(paste0(FileDir, id))) {
#       dir.create(paste0(FileDir, id))}
      
setwd(scandir)
# Write the csv file to the scan directory (where the scanner stimuli are saved)
# Move everything in this directory to your personal laptop for testing at the scanner. 
write.csv(joined, paste0(id, "_stims.csv"), row.names = FALSE, col.names = FALSE)

```





# Code for creating templates
```{r}
# temp <- read.csv("/Users/carolynmcgettigan/OneDrive - University College London/postdoc/VOCAL_ID_REPRESENTATIONS/familiarity/Gorilla/template.csv", stringsAsFactors = FALSE)
# 
# stimdir <- paste0("/Users/carolynmcgettigan/OneDrive - University College London/postdoc/VOCAL_ID_REPRESENTATIONS/familiarity/Gorilla/M26/RMS/")  # change M26 to the correct folder
# 
# stimuli <- data.frame(Filename = list.files(path=stimdir, pattern = "\\.mp3$", recursive = FALSE))
# sequences <- data.frame(Filename = list.files(path=stimdir, pattern = "\\.mp3$", recursive = TRUE))
# sequences <- sequences %>% filter(str_detect(Filename, "List")) %>% 
#              mutate(Filename = gsub("Examples/", "", Filename))
# sequences <- droplevels(sequences)
# 
# 
# data <- temp
# 
# data <- data %>% 
#     mutate(audio = sub("alexseq2", sequences$Filename[2], audio)) %>% 
#     mutate(audio = sub("alexseq", sequences$Filename[1], audio)) 
# 
# data$audio[data$ANSWER == "Alex"] <- as.character(stimuli$Filename)
# 
# data <- replace(data, is.na(data), '')
# 
# stimdir <- paste0("/Users/carolynmcgettigan/OneDrive - University College London/postdoc/VOCAL_ID_REPRESENTATIONS/familiarity/Gorilla/M10/RMS/")  # Change to correct filepath 
# 
# stimuli <- data.frame(Filename = list.files(path=stimdir, pattern = "\\.mp3$", recursive = FALSE))
# 
# data$audio[data$ANSWER == "Someone else"] <- as.character(stimuli$Filename)
# 
# write.csv(data,paste0("template_m_6.csv"), row.names = FALSE)

```






